\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-25 document/XSGRB_sample.tex

	\subsection{GRB100621A (z=0.542)}
	The data presented here also formed the basis of GCN \#
	10876\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10876.gcn3}}, 
	but not published elsewhere.
	Beginning 7.1 hours after the GRB, 2.4 ks observations reveal emission lines from \oii, \hb~and \oiii~at a common redshift of $z=0.542$.

>>>>

	\subsection{GRB100621A (z=0.542)}
	The data presented here also formed the basis of GCN \#
	10876\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10876.gcn3}}, 
	but not published elsewhere.
	Beginning 7.1 hours after the GRB, 2.4 ks observations reveal emission lines from \oii, \hb~and \oiii~at a common redshift of $z=0.542$ and a very weak afterglow continuum.

	\subsection{GRB100625A (z=0.452)}
	The data presented here is of the candidate host galaxy, taken long after the burst has faded and have not previously been published. 4.8 ks of exposure reveals a weak continuum present in all arms, but an absence of emission lines. This could indicate that the host primarily contains a older stellar population. The redshift, $z=0.452$, is taken from \citet{Fong2013}.
